Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-15 icse/paper.tex
Corrected commas and dots
Refactoring Discussion

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{0,51} & \textbf{792} \\ \midrule
\hspace{10pt} Sibling & 0.57 & 637 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Same Hierarchy & 0,55 & 22 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Superclass & 0,20 & 74 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} First Cousin & -0,02 & 53 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Ancestor & -0,65 & 6 \\ \midrule
\textbf{Common Class} & \textbf{0,01} & \textbf{2025}\\ \midrule
\hspace{10pt} Same Method & 0,01 & 762  \\
\hspace{10pt} Same Class & 0,01 & 1263 \\ \midrule
\textbf{Unrelated} & \textbf{-0,02} & \textbf{688}\\ \midrule
\hspace{10pt} No Direct Superclass & 0,08 & 289 \\
\hspace{10pt} External Superclass & -0,02 & 225  \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} No Indirect Superclass & -0,04 & 30  \\
\hspace{10pt} External Ancestor & -0,26 & 144  \\ \midrule
\textbf{Common Interface} & \textbf{-0,11} & \textbf{283} \\ \midrule
\hspace{10pt} Same Direct Interface & 0,02 & 160 \\
\hspace{10pt} Same Indirect Interface & -0,31 & 123
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}

@@

\subsection{Refactoring}

>>>>

\begin{table}[]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{0.51} & \textbf{792} \\ \midrule
\hspace{10pt} Sibling & 0.57 & 637 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Same Hierarchy & 0.55 & 22 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Superclass & 0.20 & 74 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} First Cousin & -0.02 & 53 \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Ancestor & -0.65 & 6 \\ \midrule
\textbf{Common Class} & \textbf{0.01} & \textbf{2,025}\\ \midrule
\hspace{10pt} Same Method & 0.01 & 762  \\
\hspace{10pt} Same Class & 0.01 & 1,263 \\ \midrule
\textbf{Unrelated} & \textbf{-0.02} & \textbf{688}\\ \midrule
\hspace{10pt} No Direct Superclass & 0.08 & 289 \\
\hspace{10pt} External Superclass & -0.02 & 225  \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} No Indirect Superclass & -0.04 & 30  \\
\hspace{10pt} External Ancestor & -0.26 & 144  \\ \midrule
\textbf{Common Interface} & \textbf{-0.11} & \textbf{283} \\ \midrule
\hspace{10pt} Same Direct Interface & 0.02 & 160 \\
\hspace{10pt} Same Indirect Interface & -0.31 & 123
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}

@@

\subsection{Refactoring}
In Fig.~\ref{fig:duplication} we see an increase in maintainability for refactoring larger clone classes. The tipping point, between a better maintainable refactoring and a worse maintainable refactoring, seems to lie around 28 tokens. There are fewer large clones than small clones, resulting in a very limited statistical significance on our corpus when considering clones larger than 100 tokens.

In Table \ref{tab:relation_refactor} we see the results regarding refactorings that are applied to clones with diverse relations. We see that most refactored clones are in a common class, over 54\%. This is significantly more than the percentage of clones in the common class relation as reported in Table~\ref{tab:relation}. Meanwhile, the number of refactored unrelated clones is smaller than the number reported in Table~\ref{tab:relation} (24\% -> 18\%). The main reason for this is that refactoring unrelated clones can change the relation of other clones in the same system. If we create a superclass abstraction to refactor an unrelated clone, other clones in those classes that were previously unrelated might become related.

The maintainability scores displayed in Table \ref{tab:relation_refactor} show that the most favorable clone to refactor are clones with a Sibling relation. The most unfavorable is to refactor clones to interfaces.

Regarding the return type of refactored clones, we see in Table \ref{tab:return} that this has no major impact on maintainability. A method call to the extracted method that is directly returned and no return type extracted methods are slightly more favorable than the others. We think the main reason that the ``Return'' category is on top is that when a variable is declared at the end of the cloned fragment, CloneRefactor directly returns its value and removes the declaration. This decreases volume slightly.

A higher number of parameters directly influences the corresponding metric. Because of this, we see in Fig.~\ref{fig:arguments} that more parameters negatively influence maintainability. Not only the number of parameters metric is negatively influenced, more method parameters also increase volume for the extracted method and each of the calls to it. Because of that, we see that the graph in Fig.~\ref{fig:arguments} decreases relatively rapidly.
